\paperTitle

### 2014-05-18 doc/icml2014/background.tex
Fixed a bunch of bugs

\begin{definition}[Bottleneck]
  \label{def:bottleneck}
  A hidden variable $h_i$ is said to be a \emph{bottleneck} if (i) there
  exists three observed variables (views), $x_{v_1}, x_{v_2}, x_{v_3}$,
  that are conditionally independent given $h_i$,
  and (ii) each $\mOpp{v}{i} \eqdef \Pr(x_v \mid h_i) \in \Re^{d \times k}$ has full column rank $k$
  for each $v \in \{v_1, v_2, v_3\}$.
  %Let $\sV_{h_i}$ denote any set of views for $h_i$.
  We say that a subset of hidden variables $S \subseteq \bh$ is bottlenecked
  if every $h \in S$ is a bottleneck.
  We say that a graphical model $\sG$ is bottlenecked if all its hidden variables
  are bottlenecks.
\end{definition}
For example, in \figureref{approach}, $x_1^a,x_1^b,x_2^a$ are views of the bottleneck $h_1$,
and $x_2^a,x_2^b,x_1^b$ are views of the bottleneck $h_2$.  Therefore, the clique
$\{h_1,h_2\}$ is bottlenecked.  Note that views are allowed to overlap.

>>>>

\begin{definition}[Bottleneck]
  \label{def:bottleneck}
  A hidden variable $h_i$ is said to be a \emph{bottleneck} if (i) there
  exists three observed variables (views), $x_{v_1}, x_{v_2}, x_{v_3}$,
  that are conditionally independent given $h_i$ (\figureref{bottleneck}),
  and (ii) each $\mOpp{v}{i} \eqdef \Pr(x_v \mid h_i) \in \Re^{d \times k}$ has full column rank $k$
  for each $v \in \{v_1, v_2, v_3\}$.
  %Let $\sV_{h_i}$ denote any set of views for $h_i$.
  We say that a subset of hidden variables $S \subseteq \bh$ is bottlenecked
  if every $h \in S$ is a bottleneck.
  We say that a graphical model $\sG$ is bottlenecked if all its hidden variables
  are bottlenecks.
\end{definition}
For example, in \figureref{approach}, $x_1^a,x_1^b,x_2^a$ are views of the bottleneck $h_1$,
and $x_2^a,x_2^b,x_1^b$ are views of the bottleneck $h_2$.  Therefore, the clique
$\{h_1,h_2\}$ is bottlenecked.  Note that views are allowed to overlap.

### 2014-05-18 doc/icml2014/discussion.tex
Fixed a bunch of bugs

% Bottleneck is key: previous work is preprocessing
Our approach provides consistent estimates for
a family of models in which each hidden variable is a \emph{bottleneck}---that is,
it has three conditionally independent observations.
This bottleneck property of \citet{anandkumar13tensor}
has been exploited in many other contexts,
including Latent Dirichlet Allocation \cite{anandkumar12lda},
mixture of spherical Gaussians \cite{hsu13spherical},
probabilistic grammars \cite{hsu12identifiability},
noisy-or Bayesian networks \cite{halpern2013unsupervised},
mixture of linear regressions \cite{chaganty13regression},
and others.
Each of these methods can be viewed as ``preprocessing'' the given model into a
form that exposes the bottleneck or tensor factorization structure.
The model parameters correspond directly to the solution of the factorization.

>>>>

% Bottleneck is key: previous work is preprocessing
Our approach provides consistent estimates for
a family of models in which each hidden variable is a \emph{bottleneck}---that is,
it has three conditionally independent observations.
This bottleneck property of \citet{anandkumar13tensor}
has been exploited in many other contexts,
including latent Dirichlet allocation \cite{anandkumar12lda},
mixture of spherical Gaussians \cite{hsu13spherical},
probabilistic grammars \cite{hsu12identifiability},
noisy-or Bayesian networks \cite{halpern2013unsupervised},
mixture of linear regressions \cite{chaganty13regression},
and others.
Each of these methods can be viewed as ``preprocessing'' the given model into a
form that exposes the bottleneck or tensor factorization structure.
The model parameters correspond directly to the solution of the factorization.
